Fig3

### 2020-05-07 analysis/figure-3.Rmd
better fig 4

@@

@@

a1 <- plotpc12(pca1f, pca2f, pca1f$treatment, allcolors, "Female pituitary") 
a2 <- plotpc12(pca1m, pca2m, pca1m$treatment, allcolors, "Male pituitary")
a <- plot_grid(a1,a2, labels = c("A"),label_size = 8)

bcd1 <- png::readPNG("../figures/images/fig_fig3a.png")
bcd1 <- ggdraw() +  draw_image(bcd1, scale = 1)

b2 <- plotprolactin(PRLpitF, PRLpitF$counts, "PRL", "Female gene expression") 
c2 <- makenewbargraph("pituitary", "female","eggs vs. chicks", 0, 2200)   + theme(axis.text.x = element_blank() )
d2 <- makenewbargraph("pituitary", "female", "lo vs. hi PRL   ", 0, 2200) + theme(axis.text.x = element_blank())   
b3 <- plotprolactin(PRLpitM, PRLpitM$counts, "PRL", "Male gene expression") + theme(axis.text.x = element_text())
c3 <- makenewbargraph("pituitary", "male", "eggs vs. chicks", 0, 2200)  
d3 <- makenewbargraph("pituitary", "male", "lo vs. hi PRL   ", 0, 2200)

bcd23 <- plot_grid(b2,c2,d2,b3,c3,d3, nrow = 2, rel_widths = c(2,1,1), rel_heights = c(1,1.1))

## top correlations
e <- df %>%
  arrange(desc(PRL)) %>% 
  head(10)  %>%
  mutate(PRLrounded = round(PRL, 2))%>% 
  ggplot(aes(x = reorder(rowname, PRL), y = PRL)) +
  geom_bar(stat = "identity") +
  theme_B3() +
  theme(axis.text.y = element_text(face = "italic")) +
  labs(x = " ", y = "Correlation with PRL", subtitle = "Top 10 co-regulated genes") +
  coord_flip() +
  scale_y_continuous(expand = c(0, 0))

@@

f <-  PRLDEGs %>%
  arrange(desc(lfc)) %>%
  filter(sex == "female") %>% head(10) %>% 
  ggplot(aes(x = reorder(gene, lfc), y = lfc)) + 
  geom_bar(stat = "identity", fill = "#969696") +
  theme_B3() +
  theme(axis.text.y = element_text(face = "italic")) +
  labs(x = " ", y = "Log-fold change, lo vs. hi PRL", subtitle = "Top 10 female DEGs") +
  coord_flip() +
  scale_y_continuous(expand = c(0, 0))

g <-  PRLDEGs %>%
  arrange(desc(lfc)) %>%
  filter(sex == "male") %>% head(10) %>% 
  ggplot(aes(x = reorder(gene, lfc), y = lfc)) + 
  geom_bar(stat = "identity", fill = "#525252") +
  theme_B3() +
  theme(axis.text.y = element_text(face = "italic")) +
  labs(x = " ", y = "Log-fold change, lo vs. hi PRL", subtitle = "Top 10 male DEGs") +
  coord_flip() +
  scale_y_continuous(expand = c(0, 0))

efg <- plot_grid(e,f,g, nrow = 1, labels = c("E", "F", "G"), label_size = 8)

plot_grid(a, bcd1, bcd23, efg, nrow = 4, rel_heights = c(1,1,2,1.2))

>>>>

envDEGs <- allDEG2 %>%
  filter(tissue == "pituitary", comparison == "eggs vs. chicks",
         direction == "chicks") %>%
  arrange(desc(comparison))
envDEGs

@@

## top correlations
c <- df %>%
  arrange(desc(PRL)) %>% 
  head(10)  %>%
  mutate(PRLrounded = round(PRL, 2))%>% 
  ggplot(aes(x = reorder(rowname, PRL), y = PRL)) +
  geom_bar(stat = "identity") +
  theme_B3() +
  theme(axis.text.y = element_text(face = "italic")) +
  labs(x = " ", y = "Correlation with PRL", subtitle = "Top 10 co-regulated genes") +
  coord_flip() +
  scale_y_continuous(expand = c(0, 0))

@@

a1 <- plotpc12(pca1f, pca2f, pca1f$treatment, allcolors, "Female pituitary gene expression", " ")   
a2 <- plotprolactin(PRLpitF, PRLpitF$counts, "PRL", " ") + theme(axis.text.x = element_text())

a3 <- plotpc12(pca1m, pca2m, pca1m$treatment, allcolors, "Male pituitary gene expression", NULL)
a4 <- plotprolactin(PRLpitM, PRLpitM$counts, "PRL", " ") + theme(axis.text.x = element_text())

a <- plot_grid(a1,a2,a3,a4, labels = c("A"), label_size = 8, rel_heights = c(1.1,1))

b1 <- png::readPNG("../figures/images/fig_fig3b.png")
b1 <- ggdraw() +  draw_image(b1, scale = 1)

b2 <- makenewbargraph("pituitary", "female","eggs vs. chicks", 0, 2200) + labs(subtitle = "female")  + labs(title = " ")  
b3 <- makenewbargraph("pituitary", "male", "eggs vs. chicks", 0, 2200)  + labs(subtitle = "male")  + labs(title = " ") +
  theme(axis.title.y = element_blank(), axis.ticks.y = element_blank(), 
        axis.text.y = element_blank(), axis.line.y = element_blank())

b4 <- makenewbargraph("pituitary", "male", "lo vs. hi PRL   ", 0, 2200) 
b5 <- makenewbargraph("pituitary", "female", "lo vs. hi PRL   ", 0, 2200)   + 
  theme(axis.title.y = element_blank(), axis.ticks.y = element_blank(), 
        axis.text.y = element_blank(), axis.line.y = element_blank())

b25 <- plot_grid(b2,b3,b4,b5, nrow = 2, rel_widths = c(1.2,1), rel_heights = c(1.2,1))

@@

c1 <-  plottopDEGs(envDEGs, "female", "#3A80B9", "LFC eggs vs. chicks", "Top 10 female DEGs") + labs(title = " ")
c2 <-  plottopDEGs(PRLDEGs, "male", "#3A80B9", "LFC eggs vs. chicks", "Top 10 male DEGs") + labs(title = " ")
c3 <-  plottopDEGs(PRLDEGs, "female", "#19757A", "LFC lo vs. hi PRL", NULL)
c4 <-  plottopDEGs(PRLDEGs, "male", "#19757A", "LFC lo vs. hi PRL", NULL)

b <- plot_grid(b1,b25,nrow = 1, rel_widths = c(1.2,1))

c <- plot_grid(c1,c2,c3,c4, align = "v" , rel_heights = c(1.2,1))

bc <- plot_grid(b,c, labels = c("B","C"), label_size = 8, rel_widths = c(1.2,1))

fig3 <- plot_grid(a, bc, nrow = 2, rel_heights = c(1,1))
fig3

#pdf(file="../figures/fig3.pdf", width=7.25, height=7.25)
#plot(fig3)
#dev.off()
```
